Formal Verification of Real Models from Platforms Using The B-method

### 2009-04-27 papers/FM2009/source/paper.tex
almost finishing the related works

There are in the literature of computer science some technics\cite{BHDL_2003,GEMPLUS_99} to model hardware
and the virtual machines using the B method. Then, the B method has been used successfully to model the
operational semantic, however The cost modeling was still too expensive and this paper describes some
techniques to lower the cost modeling. In general, the researchers are concetrated at model the Java
Virtual Machine (JVM), but it is not easy to specify  it, because it very complex, and become more
difficult to write good lemmas, to normalize the functions and to verify the properties. Then, this
technique specify a model more simple to get better results. Besides, the objectives are to get concret
results fastly and, in the same time, stay near to model of actual processors.
% Re-uso  - modularization
The most of related works are specific to one plataform and its basic definitions cannot be re-used at in
other platforms. The used strategy created a good logic separation about the concepts of modelling. Thus,
the basic projects, the Hardware and Types Library, have functions with a low coupling and high
cohesion, that promove the re-use. Soon, these re-use better too the code generation and prove
process.{{Pare aqui \ssssssss }}

 [Uma das grandes vantagens é a evolução suporte ao método B]

 A other advantage of this work is the use of news and advanceds funcionalities of B method. The first is
 the paralelization of prove procces and  the second is instensive use of math patterns associated with proof
 commands. In the

@@

>>>>

There are in the literature of computer science some technics\cite{BHDL_2003,GEMPLUS_99} to model hardware and the
virtual machines using the B method. Then, the B method has been used successfully to model the operational
semantic, however the cost of modeling was still expensive and this paper describes some techniques to lower the
cost modeling.

In general, the researchers are concetrated at model the Java Virtual Machine (JVM), but it is not easy to specify 
it, because it very big and complex, and become more difficult to write good lemmas, to normalize the functions and
to verify its properties. Then, this work specify a model more simple to get better results fastly, in the same
time, stay near to model of actual processors.
% Re-uso  - modularization
The most of related works are specific to one plataform\cite{GEMPLUS_99,ammm} and its basic definitions cannot be
re-used at in other platforms. The used strategy created a good logic separation about the concepts of modelling.
Thus, the basic projects, the Hardware and Types Library, have functions with a low coupling and high cohesion, that
promove the re-use. Soon, these re-use better too the code generation, the confiability and prove process.

 Others advantages of this work are the use of news and advanceds funcionalities of B method. Normaly, the related
 works don`t enjoy this funcionalities, because these are news and required advanced knowleadge about tools for B
 method. These advantages are the paralelization of prove proccess and the instensive use of math patterns
 associated with proof commands.

@@

Quais as desvantagens/problemas com relaçao aos outros?
-The B method is not good to verify all kindy of cararacteristics.
-The our results are not mature, b 
-Actually, we don`t define 
-The B method can verify many diferentes properties of model, but some properties cannot be easy to verify and
model.
 -Some times, the B method is very dificult to model, eventually a other metodology can verify
